Numerical simulation of bubble deformation \\ and breakup under simple linear shear flows

### 2024-11-29 Revised-paper/Reply/Reply-Reviewer1.tex

Changes made in response to comments of Reviewer 1: \begin{enumerate}
%%1
\item
\textsf
{Abstract, hightlights, and introduction are written in a way that confuses the reader: the text jumps back and forth between bubbles and drops as well as shear flows and other flow configurations. Then it suddenly moves to lift and deformation rather than breakup. Finally a number of random applications are mentioned without any relation to bubble breakup. The authors should clearly state what their contrbution is from the outset. The reader will not go on until the end to figure that out by himself. The use of shorter paragraphs each addressing a single issue is very helpful.}
\vspace{3 mm}

Response: \\
In the revision, we made many improvements to the grammar and structure so that the reader can follow in a much more efficient manner. \\
\\

%%2
\item
\textsf
{Method: The use of only 2 levels of grid refinement appears odd. For an accurate representation of the flow near the interface a very fine mesh is typically needed. Only 32 cells over the bubble diameter is hardly sufficient ot get accurate results as corroborated by the mediorce agreement of the presented simulation results with the experimental data used for validation. Two more levels of grid refinement are likely needed to resolved the flow near the bubble while farther away some coarsening may be possible. Optimizing the grid is imperative in a situaltion like the considerd one due to the strong deformation of the bubble which high curvature of the interface and the singular nature of the breakup event. Fully capturing the breakup, which represents a topological singularity, is impossible without a subgrid scale model.}
\vspace{3 mm}

Response: \\
In addition to the previous verification and validation tests (Tables I and II, Figure 3), we now list a number of references (top of section 3.2) involving bubbles and drops with severe deformation in which our method is validated by way of grid refinement studies and comparison with experiments.

In light of all the previous tests that we have already done, with satisfactory results, it is grossly unfair to require us to do a further grid refinement which would force us to wait another four years for the results; please see Remark 1 in section 3.1.  It is also very unfair to ask us to test a subgrid scale model which is very unnecessary for our problem; please see Remark 2 in section 3.1.  As explained throughout our article, our results fulfill a unique niche in bubble dynamics (low Capillary number, high Reynolds number),  that is on the one hand important in many applications (see first paragraph in the introduction, we have added many new references) and yet impossible to do controlled experiments unless one is in a microgravity environment.  If our paper is rejected because of this, it is most certain that someone else will publish similar findings later on, which is terribly unfair to us.  As we now mention in the conclusion, we expect many follow-on articles should our article be accepted;  For example bubble deformation with non-Newtonian matrix fluids, experimenting with a non-spherical initial condition (your recommendation), bubble deformation in complex geometry, etc.

@@

%%3
\par\noindent
\item
\textsf
{Results: Mostly just pictures are shown from which little is to be learned. The only results of which future use can be expected is the regime map in Fig. 12. Bu this is also only qualitative and based on very few data points. More combinations of Ca and Re should be provided and a quantitative fit to the regime boundary be obtained. Moreover only two values of density and viscosity ratio equal to 1 and ~0.001 are used. An investigation of intermediate values would be straight forward and would allow to provide also models for the influence of these obviously important parameters. In particular it should be clarified whether the difference in behavior is more due to the density ration or more due to the viscosity ratio. Also it needs to be investigated how small these ratios need to be for the gas phase properties to be considered as negligibly small. For the practically important case of air bubbles in water the viscosity ratio is 0.02, an order of magnitude larger than considered in the paper. Whether this can already be considered negligible or not remains unclear.}
\vspace{3 mm}

Response: \\
As in our response to the previous comment, we believe it is unfair to ask us to  report more results; each new data point requires an additional 6 months, and additional computers.  As also mentioned in our response to point 2 above, and hilighted in our revised introduction, our work as it stands now is significant and novel.  We take the referee comments on as a challenge for future work.  Please refer to the revised conclusions section in which we report on potential future work.

The reviewer says ``Mostly just pictures are shown from which little is to be learned,''  but yet it is clearly mentioned that the shear force necessary to deform a bubble is noticeably larger than that for the drop, all other factors being equal, and from the results (figures and tables) we deduce for the first time the mechanisms for why the bubble requires a larger shearing force; please see section 4.3 second to last paragraph.

Just in case the reviewer overlooked these additional points of significance and novelty:
\begin{enumerate}
\item The behavior of the bubble deformation process around critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
\item The behavior of the bubble breakup process at critical $Re$ conditions with $Ca$ = 0.3  $\sim$ 1.0 has been presented for the first time.
\item The value of critical $Re$ numbers was found for $Ca$ = 0.3  $\sim$ 1.0 for the first time.
\item  We showed that most previous computational studies overestimated drop deformation and breakup because most previous studies used a domain size with $W$ (width ($y$directional length)) =4$R$. Drop deformation is promoted when using a domain size with $W=4R$. 
\item The difference in the deformation and breakup between the bubble ($\lambda<<1$) and the drop ($\lambda = 1$ and $\eta = 1$) was clearly shown.
\item Shear-induced bubble/drop breakup critical curves were obtained. 
\end{enumerate}

Regarding the effect of $\lambda$ and $\eta$, ongoingly we are examining the effect of $\lambda$ and $\eta$ on drop breakup for following 
combinations of $\lambda$ and $\eta$:
\begin{tabbing}
 \hspace{55mm} \= \hspace{10mm} \kill
 \hspace{5mm} 1. $\lambda$ = 1.0, $\eta$ =1.0 (done) \> 2. $\lambda \simeq 0.0$, $\eta \simeq 0.0$ (this study) \\ 
 \hspace{5mm} 3. $\lambda$ = 1.0, $\eta \simeq 0.0$ (done) \> 4. $\lambda$ = 1.0, $\eta$ =0.01 \\
 \hspace{5mm} 5. $\lambda$ = 1.0, $\eta \simeq 0.1$ \> 6. $\lambda$ = 0.1, $\eta \simeq 0.0$ (done) \\
 \hspace{5mm} 7. $\lambda$ = 0.1, $\eta$ =0.01 \> 8. $\lambda = 0.1$, $\eta$ =0.1  \\
 \hspace{5mm} 9. $\lambda$ = 0.1, $\eta$ =1.0 (done) \> 10. $\lambda$ = 1.0, $\eta$ =10  \\
 \hspace{5mm} 11. $\lambda$ = 1.0, $\eta$ =100 \> 12. $\lambda$ = 1.0, $\eta$ =1000 \\
\end{tabbing}

### 2024-11-29 Revised-paper/Paper/Bubble-deformation-Rev.tex
working on the replies

\author[1,2]{Mitsuhiro Ohta\corref{cor1}} 
\cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
\affiliation[1]{
  organization={Department of Mechanical Science, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\affiliation[2]{
  organization={Department of Mechanical Engineering, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}

@@

\affiliation[3]{
  organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
  addressline={2-1 Hyakuyama, Mishimagun Shimamoto-cho},
  state={Osaka 618-0021}, 
  country={Japan}}

@@

\author[4]{Edwin Jimenez}  
\affiliation[4]{
  organization={Spectral Numerical, LLC},
  addressline={1942 Broadway St., STE 314C},
  city={Boulder},
  state={CO 80302},
  country={USA}}

\author[5]{Mark Sussman}  
\affiliation[5]{
  organization={Department of Mathematics, Florida State University},
  city={Tallahassee},
  state={FL 32306},
  country={USA}}

@@

	We remark that there have been a number of computational articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  We reiterate, though, that for bubble deformation and breakup in shear flows, only a few computational articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.  These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.  Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented one numerical result for a bubble breakup process under the condition of $Ca$ (capillary number) = 35. Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.  We point out that all of the previous computational research on bubble deformation (and breakup) under shear driven flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2} use the (explicit) Lattice Boltzmann method.  For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.  We contend that a projection method (i.e. this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.  Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}, maintains the gas/liquid interface as sharp, enables accurate approximation of the surface tension force,  and by construction the CLSVOF method preserves mass and volume within a fraction of a percent. The results that we present in this article (see e.g. section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data (where available) and grid refinement studies.  Admittadly, each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$!), oscillatory behaviour is observed delaying the determination of breakup or not.  Finally, the larger the deformation parameter $D$, the longer one must make the computational domain (and thereby leading to larger domain aspect ratio) thereby adversely effecting the condition number even more for carrying our the pressure projection. 

@@

\textcolor{red}
{
	We remark that our method is a ``sharp interface method\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00}.  Thereby we do not need to specify an empirical interface thickness parameter\cite{SusSmeOsh94,SusPuc00}.
}

%
%%
%\begin{eqnarray}
%\nabla\cdot\bmu=0  \label{divu} %\\
%\end{eqnarray}
%%
%\begin{eqnarray}
%\frac{\partial\bmu}{\partial t}+(\bmu\cdot\nabla)\bmu=
%\frac{1}{\rho}\nabla\cdot(-p\bmI+2\mu\bmD)+\bmg-
%\frac{\sigma\kappa}{\rho}\nabla H  \label{nseqn}
%\end{eqnarray}
%
\par
$\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure, $\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor ($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$ is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The singular Heaviside gradient term in the right-hand side of equation~\eqref{nseqn} is a body force representing the surface tension force and is equivalent to specifying that the jump in the normal stress is equal to $\sigma\kappa$ (\citet{TanguyEtAl2007}).  The surface tension force expressed by the singular Heaviside gradient term acts only on the gas-liquid interface.  The sharp interface ``Ghost Fluid Method'' (\citet{KanFedLiu00}) is used to discretize the gradient of the Heaviside function as it appears in the surface tension force term.  This force, upon discretization, is only non-zero across cells in which the level set function changes sign.
\par
The interfacial curvature $\kappa$ is computed with second-order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).  We remark that we would get the same results if we compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
\par
Since $\rho$ and $\mu$ are taken to be constant in each fluid, with a jump at
the interface, they can be expressed in terms of the Heaviside function,
%
\begin{eqnarray}\label{rhomu}
  \rho=\rho_{\rm m}\Hea+\rho_{\rm b}(1-\Hea), \qquad 
  \mu=\mu_{\rm m}\Hea+\mu_{\rm b}(1-\Hea).
\end{eqnarray}
%
The subscripts ``b'' and ``m'' refer to ``bubble'' (or drop) and ``matrix fluid.'' To represent the free surface with the CLSVOF method, we must evolve the solution to both the VOF equation for $F$ and the LS equation for $\phi$:
%
%\begin{subequations}\label{eq:clsvof}
\begin{align}\label{eq:clsvof}
  \frac{\partial F}{\partial t}+(\bmu\cdot\nabla)F = 0, \qquad 
  \frac{\partial \phi}{\partial t}+(\bmu\cdot\nabla)\phi = 0. 
\end{align}
%\end{subequations}
%
In all computations, the discretized variables $p$, $\phi$, and $F$ are located at the cell centers, and the discrete velocity variable $\bmu$ is located at the cell face centers.  Our computations are performed using an overall second-order accurate hydrodynamic scheme.  The spatial discretization uses second-order accurate, slope-limited, upwind techniques for the nonlinear advective terms.  The velocity and pressure fields are computed using an implicit pressure projection procedure.
\par
The temporal discretization of our numerical method is an operator split projection method as described by \citet{SusSmiHusOhtZhi07}.  An outline of our method is as follows (see \citet{SusSmiHusOhtZhi07}, section 4, for more details):
\begin{description}
\item[All Steps. Timestep] 
 \begin{eqnarray*}
 \end{eqnarray*}
  The timestep, $\Delta t$, is governed by the CFL condition and
  surface tension (section 5.7 of \citet{SusSmiHusOhtZhi07}):
 \begin{eqnarray*}
 \Delta t < \min_{i,j,k} \left( \frac{\Delta x}{2|U^{n}|},
   \frac{1}{2}\sqrt{\frac{\rho^{L}}{8\pi\sigma}}\Delta x^{3/2}\right)
 \end{eqnarray*}

@@

\textcolor{red}
{
The previous section discussed bubble deformation and breakup. Large deformation and breakup of the bubble are expected to be closely related to the state of shear stress acting on the bubble.  Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds number equal to 50 and 93.  The shear stress profile on the left corresponds to the case of $Re = 50$, and the right side shows the shear stress profile for the case of $Re = 93$.  The normalized shear stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a ratio of the local shear stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress $\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$ condition, the same value of $\tau_{0}$ is used regardless of $Re$.  For the case of $Re = 50$, the bubble reached a deformed stable state, and the shear stress profile around the bubble was drawn after the bubble attained a stable deformed state.  As observed in previous sections, when the value of $Re$ is slightly below the critical $Re$ condition, the bubble does not settle into a deformed stable state. Instead, it alternates in an elongation and contraction process.  The shear stress profile for the case of $Re$ = 93 was depicted when the bubble sufficiently elongated ($T$ = 14.9).  In comparison to the $Re=50$ case on the left, the right image in Fig.~\ref{fig:ShearStress} ($Re=93$) shows a higher shear stress profile near the bubble endpoints as it undergoes an elongation state in the process toward breakup.  The value of the maximum shear stress for the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ and the maximum shear stress for the case of $Re = 93$ at the moment shown in Fig.~\ref{fig:ShearStress} has the value of $\tau ^{\ast} \approx 8$.  The shear stress profile in Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from $\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions with $\tau ^{\ast} \geqq 6$ are illustrated in red.  As shown in the figure, the strongest shear stresses are concentrated on the ends of the bubble for both $Re$ conditions.  This indicates that the strong shear stresses acting on the ends of the bubble are responsible for much of the bubble stretching.  It is important to note that the magnitude of the shear stress acting on the ends of the bubble for the case of $Re = 93$ is much larger than that for the case of $Re = 50$.  
}

We also observed that the shear stress inside the bubble was very small relative to that of the matrix fluid due to the bubble's very small density and viscosity. Since the force of strong shear stresses acting on the ends of the bubble is difficult to transfer across the interface, a sufficiently large $Re$ condition is required for large bubble deformations.

>>>>

\author[1,2]{Mitsuhiro Ohta\corref{cor1}} 
\cortext[cor1]{Corresponding author: m-ohta@tokushima-u.ac.jp}
\begin{comment} 
\affiliation[1]{
  organization={Department of Mechanical Science, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\affiliation[2]{
  organization={Department of Mechanical Engineering, Graduate School of Technology, 
                Industrial and Social Sciences, Tokushima University},
  addressline={2-1 Minamijyousanjima-cho},
  state={Tokushima 770-8506}, 
  country={Japan}}
\end{comment}

@@

\begin{comment} 
\affiliation[3]{
  organization={High Performance Plastics Company, Sekisui Chemical Co., Ltd.},
  addressline={2-1 Hyakuyama, Mishimagun Shimamoto-cho},
  state={Osaka 618-0021}, 
  country={Japan}}
\end{comment}

@@

\author[4]{Edwin Jimenez}  
\begin{comment} 
\affiliation[4]{
  organization={Spectral Numerical, LLC},
  addressline={1942 Broadway St., STE 314C},
  city={Boulder},
  state={CO 80302},
  country={USA}}
\end{comment}

\author[5]{Mark Sussman}  
\begin{comment} 
\affiliation[5]{
  organization={Department of Mathematics, Florida State University},
  city={Tallahassee},
  state={FL 32306},
  country={USA}}
\end{comment}

@@

	We remark that there have been a number of computational articles on the study of lift of slightly deformable bubbles\cite{ErvinANDTryggvason1997,legendre1998lift}.  We reiterate, though, that for bubble deformation and breakup in shear flows, only a few computational articles exist: \cite{WeiQiaXu12,WanShiZha15,AAMM-16-2}.  These previous studies mainly examined the dynamics (e.g., rotation angle) of bubble deformation in shear flow.  Concerning bubble breakup, Wei et al.~\cite{WeiQiaXu12} presented one numerical result for a bubble breakup process under the condition of $Ca$ (capillary number) = 35. Sharifi et al\cite{AAMM-16-2} presented two results for bubble breakup corresponding to $Ca=7.5$ and $Ca=11.2$.  We point out that all of the previous computational research on bubble deformation (and breakup) under shear driven flow\cite{WeiQiaXu12,WanShiZha15,AAMM-16-2} use the (explicit) Lattice Boltzmann method.  For accurately computing the tensile strength of a bubble, and accurately computing threshold parameters for break-up (what we do in this article, and what was not done in previous work), it is critical that a numerical method directly enforces the velocity continuity condition and the gas-liquid interface normal jump conditions.  We contend that a projection method (i.e. this paper and \cite{zhang2021three,zhang2022three,OhtSus12}) is the more appropriate (albeit slower) method for our study rather than the Lattice Boltzmann method.  Also, in contrast to the Lattice Boltzmann method, our interface ``capturing'' method, the CLSVOF method\cite{SusPuc00,SusSmiHusOhtZhi07}, maintains the gas/liquid interface as sharp, enables accurate approximation of the surface tension force,  and by construction the CLSVOF method preserves mass and volume within a fraction of a percent. The results that we present in this article (see e.g. section \ref{convergence}) regarding measuring the tensile strength of a bubble are unique and validated with respect to comparisons with previous experimental data (where available) and grid refinement studies.  Each simulation on the finest resolution takes over a half a year to complete on a workstation because of the following unavoidable factors: (i) the large density-ratio projection method requires the solution of a large sparse, ill-conditioned, matrix system at each time step, (ii) the finer the mesh, the more precise the measured threshold, and right at the threshold (Taylor Deformation parameter $D\approx 1$), oscillatory behaviour is observed delaying the determination of breakup or not.  Finally, the larger the deformation parameter $D$, the longer one must make the computational domain (and thereby leading to larger domain aspect ratio) thereby adversely effecting the condition number even more for carrying our the pressure projection. 

@@

\textcolor{red}
{
	We note that our method is a ``sharp interface method\cite{SusSmiHusOhtZhi07,Sus03,KanFedLiu00}.  Thereby we do not need to specify an empirical interface thickness parameter\cite{SusSmeOsh94,SusPuc00}.
}

%
%%
%\begin{eqnarray}
%\nabla\cdot\bmu=0  \label{divu} %\\
%\end{eqnarray}
%%
%\begin{eqnarray}
%\frac{\partial\bmu}{\partial t}+(\bmu\cdot\nabla)\bmu=
%\frac{1}{\rho}\nabla\cdot(-p\bmI+2\mu\bmD)+\bmg-
%\frac{\sigma\kappa}{\rho}\nabla H  \label{nseqn}
%\end{eqnarray}
%
\par
$\bmu$ is the velocity vector, $t$ represents time, $p$ is the pressure, $\bmI$ is the unit tensor, $\bmD$ is the rate of deformation tensor ($\bmD=\frac{1}{2}(\nabla\bmu+(\nabla\bmu)^{T})$), $\rho$ is the density, $\mu$ is the viscosity, $\kappa$ is the interfacial curvature, and the Heaviside function $\Hea(\phi)$ is a function of the level set (LS) function $\phi$. The singular Heaviside gradient term in the right-hand side of equation~\eqref{nseqn} is a body force representing the surface tension force and is equivalent to specifying that the jump in the normal stress is equal to $\sigma\kappa$ (\citet{TanguyEtAl2007}).  The surface tension force expressed by the singular Heaviside gradient term acts only on the gas-liquid interface.  The sharp interface ``Ghost Fluid Method'' (\citet{KanFedLiu00}) is used to discretize the gradient of the Heaviside function as it appears in the surface tension force term.  This force, upon discretization, is only non-zero across cells in which the level set function changes sign.
\par
The interfacial curvature $\kappa$ is computed with second-order accuracy directly from the volume-of-fluid (VOF) function and the level set function using the height function technique (\citet{Sus03,SusSmiHusOhtZhi07}).  We note that we would get the same results if we compute $\kappa$ directly from the LS function using the ``level set'' height function technique.
\par
Since $\rho$ and $\mu$ are taken to be constant in each fluid, with a jump at
the interface, they can be expressed in terms of the Heaviside function,
%
\begin{eqnarray}\label{rhomu}
  \rho=\rho_{\rm m}\Hea+\rho_{\rm b}(1-\Hea), \qquad 
  \mu=\mu_{\rm m}\Hea+\mu_{\rm b}(1-\Hea).
\end{eqnarray}
%
The subscripts ``b'' and ``m'' refer to ``bubble'' (or drop) and ``matrix fluid.'' To represent the free surface with the CLSVOF method, we must evolve the solution to both the VOF equation for $F$ and the LS equation for $\phi$:
%
%\begin{subequations}\label{eq:clsvof}
\begin{align}\label{eq:clsvof}
  \frac{\partial F}{\partial t}+(\bmu\cdot\nabla)F = 0, \qquad 
  \frac{\partial \phi}{\partial t}+(\bmu\cdot\nabla)\phi = 0. 
\end{align}
%\end{subequations}
%
In all computations, the discretized variables $p$, $\phi$, and $F$ are located at the cell centers, and the discrete velocity variable $\bmu$ is located at the cell face centers.  Our computations are performed using an overall second-order accurate hydrodynamic scheme.  The spatial discretization uses second-order accurate, slope-limited, upwind techniques for the nonlinear advective terms.  The velocity and pressure fields are computed using an implicit pressure projection procedure.
\par
The temporal discretization of our numerical method is an operator split projection method as described by \citet{SusSmiHusOhtZhi07}.  An outline of our method is as follows (see \citet{SusSmiHusOhtZhi07}, section 4, for more details):
\begin{description}
\item[All Steps. Timestep] 
 \begin{eqnarray*}
 \end{eqnarray*}
  The timestep, $\Delta t$, is governed by the CFL condition and
  surface tension (section 5.7 of \citet{SusSmiHusOhtZhi07}):
 \begin{eqnarray*}
 \Delta t < \min_{i,j,k} \left( \frac{\Delta x}{2|U^{n}|},
   \frac{1}{2}\sqrt{\frac{\rho^{L}}{8\pi\sigma}}\Delta x^{3/2}\right)
 \end{eqnarray*}

@@

\textcolor{red}
{
The previous section discussed bubble deformation and breakup. Large deformation and breakup of the bubble are expected to be closely related to the state of shear stress acting on the bubble.  Figure~\ref{fig:ShearStress} shows the shear stress profile around a bubble for two Reynolds numbers under the condition of $Ca = 0.3$: Reynolds number equal to 50 and 93.  The shear stress profile on the left corresponds to the case of $Re = 50$, and the right side shows the shear stress profile for the case of $Re = 93$.  The normalized shear stress, $\tau^{\ast} = \tau / \tau_{0}$, is defined as a ratio of the local shear stress $\tau = \mu_{\rm m}$$\sqrt{2\bmD:\bmD}$ and the apparent shear stress $\tau_{0} = \mu_{\rm m}$$\mathit{\Gamma}$.  In this study, for a given $Ca$ condition, the same value of $\tau_{0}$ is used regardless of $Re$.  For the case of $Re = 50$, the bubble reached a deformed stable state, and the shear stress profile around the bubble was drawn after the bubble attained a stable deformed state.  As observed in previous sections, when the value of $Re$ is slightly below the critical $Re$ condition, the bubble does not settle into a deformed stable state. Instead, it alternates in an elongation and contraction process.  The shear stress profile for the case of $Re$ = 93 was depicted when the bubble sufficiently elongated ($T$ = 14.9).  In comparison to the $Re=50$ case on the left, the right image in Fig.~\ref{fig:ShearStress} ($Re=93$) shows a higher shear stress profile near the bubble endpoints as it undergoes an elongation state in the process toward breakup.  The value of the maximum shear stress for the case of $Re = 50$ is $\tau ^{\ast} \approx 6$ and the maximum shear stress for the case of $Re = 93$ at the moment shown in Fig.~\ref{fig:ShearStress} has the value of $\tau ^{\ast} \approx 8$.  The shear stress profile in Fig.~\ref{fig:ShearStress} (color contour) is drawn in the range from $\tau^{\ast} = 1$ to $\tau ^{\ast} = 8$, but, for emphasis, shear stress regions with $\tau ^{\ast} \geqq 6$ are illustrated in red.  As shown in the figure, the strongest shear stresses are concentrated on the ends of the bubble for both $Re$ conditions.  This indicates that the strong shear stresses acting on the ends of the bubble are responsible for much of the bubble stretching.  It is important to note that the magnitude of the shear stress acting on the ends of the bubble for the case of $Re = 93$ is much larger than that for the case of $Re = 50$.  
}
\par
\textcolor{red}
{
We also observed that the shear stress inside the bubble was very small relative to that of the matrix fluid due to the bubble's very small density and viscosity. Since the force of strong shear stresses acting on the ends of the bubble is difficult to transfer across the interface, a sufficiently large $Re$ condition is required for large bubble deformations.
}
